Checkpoint 3

### 2020-04-22 Checkpoint3.Rmd
Update Checkpoint3.Rmd

---
title: "Checkpoint 3"
author: ""
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---
# Data
```{r}
save(states_cases_data, file = 'states_cases_data.RData')
dim(states_cases_data)
names(states_cases_data)
head(states_cases_data)
summary(states_cases_data)
```

>>>>

---
title: "Checkpoint 3"
author: "Quinn Rafferty, Ferderico Chung, Sofia Pozsonyiova, Will Madairy"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc:true
    toc_float:true
---

\
\

#Libraries

```{r, warning=FALSE}
library(dplyr)
library(usmap)
library(maps)
library(ggplot2)
library(tidyverse)
library(ggmap)
library(viridis)
library(rgdal)
```

\
\

# Data
```{r}
load("FullDataSet.csv")
```

Re-Cleaned 
```{r}
FullDataSet <- FullDataSet %>% select(-c(median_rent))
```

##Dataset Description 
**Put in Data Descriptions Here**

##Dataset Details 
```{r}
dim(FullDataSet)

names(FullDataSet)

head(FullDataSet)

summary(FullDataSet)

colnames(FullDataSet)
```

##Visualizations

\
\

#Analysis
